%-------------------------
% Resume in Latex
% Author : Abey George
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{ \vspace{-4pt}\scshape\raggedright\large\bfseries }{}{0em}{}[
\color{black}
\titlerule
\vspace{-5pt}
]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{ \item\small{ {#1 \vspace{-2pt}} } }

\newcommand{\classesList}[4]{ \item\small{ {#1 #2 #3 #4 \vspace{-2pt}} } }

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}
\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
  \textbf{\large#1} & \textbf{\small #2} \\
  \textit{\large#3} & \textit{\small #4} \\
\end{tabular*}
\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{ \item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \textit{\small#1} & \textit{\small #2} \\
\end{tabular*}
\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{ \item
\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
  \small#1 & \textbf{\small #2} \\
\end{tabular*}
\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}
\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}
\vspace{-5pt}}

\newcommand{\sbullet}[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
  %----------HEADING----------

  \begin{center}
    {\Huge \scshape Purbayan Pramanik} \\
    \vspace{1pt}
    Kolkata, West Bengal \\
    \vspace{1pt}
    \small
    \href{mailto:purbayan.dev@gmail.com}{\raisebox{-0.2\height}{\faEnvelope}\  \underline{Gmail}}
    ~
    \href{https://www.linkedin.com/in/purbayan-pramanik-30586124b/}{\raisebox{-0.2\height}{\faLinkedinSquare}\ \underline{Linkedin}}
    ~
    \href{https://github.com/PPRAMANIK62}{\raisebox{-0.2\height}{\faGithub}\ \underline{GitHub}}
    ~
    \href{https://x.com/ppramanik62}{\raisebox{-0.2\height}{\faTwitter}\ \underline{X}}
    ~
    \href{https://purbayan-dev.pages.dev}{\raisebox{-0.2\height}{\faGlobe}\ \underline{Portfolio}}
  \end{center}
  \vspace{0.5mm}

  %-----------EDUCATION-----------
  \section{EDUCATION}
  \resumeSubHeadingListStart \resumeSubheading {National Institute Of Technology Durgapur}{2022 -- 2026}
  {B.Tech - Mechanical Engineering}{Durgapur, West Bengal} \resumeSubHeadingListEnd

  %-----------TECHNICAL SKILLS-----------
  \section{TECHNICAL SKILLS}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{ \textbf{\normalsize{Skills:}}{ \normalsize{Full Stack Development, Systems Programming, Open Source, Linux Customization}} \\ \textbf{\normalsize{Languages:}}{ \normalsize{TypeScript, Rust, C, Go, JavaScript, Shell, Python}} \\ \textbf{\normalsize{Web Technologies:}}{ \normalsize{React, Next.js, Tailwind CSS, Node.js, Express.js, HTML, CSS, ShadCN-UI, Framer Motion}} \\ \textbf{\normalsize{Systems \& Low-Level:}}{ \normalsize{TCP Networking, FFT/DSP, TF-IDF Search Algorithms, Concurrency, Audio Processing}} \\ \textbf{\normalsize{Developer Tools:}}{ \normalsize{Git, Docker, Linux, Hyprland, Zed, Neovim, VS Code, GitHub, Postman, Vercel, Bun}} \\ \textbf{\normalsize{Databases:}}{ \normalsize{PostgreSQL, MongoDB, Supabase, Firebase}} \\ }}
  \end{itemize}
  \vspace{-15pt}

  %-----------PROJECTS-----------
  \section{PROJECTS}
  \vspace{-5pt}
  \resumeSubHeadingListStart \resumeProjectHeading {\href{https://github.com/PPRAMANIK62/wayforged}{\textbf{\large{\underline{wayforged}}} \href{https://github.com/PPRAMANIK62/wayforged}{\raisebox{-0.1\height}{\faExternalLink} }} $|$ \large{\underline{Shell, TUI, charmbracelet/gum, Hyprland, Linux}}}{2025}\\
  \resumeItemListStart \resumeItem{\normalsize{TUI-based installer for a complete Fedora Hyprland development environment, powered by charmbracelet/gum.}}
  \resumeItem{\normalsize{14 installation phases covering 22 config files with three install modes (full, minimal, custom).}}
  \resumeItem{\normalsize{Idempotent design with error recovery — retry, skip, or view logs on any phase failure.}}
  \resumeItemListEnd
  \vspace{-20pt}
  \resumeProjectHeading
  {\href{https://canvas-kit.vercel.app}{\textbf{\large{\underline{Canvas Kit}}} \href{https://github.com/PPRAMANIK62/canvas-kit}{\raisebox{-0.1\height}{\faExternalLink} }} $|$ \large{\underline{TypeScript, Next.js 15, React 19, Tailwind CSS, Canvas API}}}{2025}\\
  \resumeItemListStart \resumeItem{\normalsize{Lightweight drawing application with multiple tools (Brush, Eraser, Rectangle, Circle) and keyboard shortcuts.}}
  \resumeItem{\normalsize{Layer system with reordering, visibility toggles, color palette, opacity controls, and PNG export.}}
  \resumeItem{\normalsize{Built with Next.js 15 and React 19, deployed on Vercel.}}
  \resumeItemListEnd
  \vspace{-20pt}
  \resumeProjectHeading {\href{https://github.com/PPRAMANIK62/4at}{\textbf{\large{\underline{4at}}} \href{https://github.com/PPRAMANIK62/4at}{\raisebox{-0.1\height}{\faExternalLink} }} $|$ \large{\underline{Rust, Go, TCP, Concurrency}}}{2025}\\
  \resumeItemListStart \resumeItem{\normalsize{Multi-user TCP chat server built from raw sockets — no frameworks. Dual implementation in Rust and Go.}}
  \resumeItem{\normalsize{Token-based authentication, rate limiting, ban system, and broadcast messaging.}}
  \resumeItem{\normalsize{Compares OS threads (Rust std::thread) vs green threads (Go goroutines) for concurrent connections.}}
  \resumeItemListEnd
  \vspace{-20pt}
  \resumeProjectHeading
  {\href{https://github.com/PPRAMANIK62/seroost}{\textbf{\large{\underline{seroost}}} \href{https://github.com/PPRAMANIK62/seroost}{\raisebox{-0.1\height}{\faExternalLink} }} $|$ \large{\underline{Rust, TF-IDF, HTTP, JavaScript}}}{2025}\\
  \resumeItemListStart \resumeItem{\normalsize{Local search engine that indexes documents using TF-IDF, ranks by relevance, and serves results over HTTP.}}
  \resumeItem{\normalsize{Custom implementation — no search library. Tokenization, inverted index, TF-IDF scoring from scratch.}}
  \resumeItem{\normalsize{Full-stack: Rust backend with only 3 external crates, JavaScript/HTML web frontend.}}
  \resumeItemListEnd
  \vspace{-20pt}
  \resumeProjectHeading {\href{https://github.com/PPRAMANIK62/musializer}{\textbf{\large{\underline{musializer}}} \href{https://github.com/PPRAMANIK62/musializer}{\raisebox{-0.1\height}{\faExternalLink} }} $|$ \large{\underline{C, FFT, raylib, DSP}}}{2025}\\
  \resumeItemListStart \resumeItem{\normalsize{Real-time audio frequency spectrum visualizer using custom FFT implementation (\textasciitilde670 lines of C).}}
  \resumeItem{\normalsize{Header-only FFT library with 256 frequency bins at 44,100 Hz sample rate, O(N log N) complexity.}}
  \resumeItem{\normalsize{Single external dependency (raylib). Visualizes audio decomposition into frequency components in real time.}}
  \resumeItemListEnd \resumeSubHeadingListEnd
  \vspace{-12pt}

  %-----------OPEN SOURCE-----------
  \section{OPEN SOURCE}
  \resumeSubHeadingListStart \resumeItemListStart \resumeItem{\normalsize{Contributor to \textbf{Apache ECharts} (65,000+ stars) — the largest open source charting library.}}
  \resumeItem{\normalsize{Contributed to the \textbf{shadcn ecosystem} through \textbf{fiddle-factory} — component library PRs.}}
  \resumeItemListEnd \resumeSubHeadingListEnd
  \vspace{-12pt}

  %-----------INTERNSHIP-----------
  \section{INTERNSHIP}
  \resumeSubHeadingListStart \resumeSubheading
  {fiddle-factory \href{https://github.com/fiddle-factory}{\raisebox{-0.1\height}{\faExternalLink} }}{Dec 2025 -- Ongoing}
  {\underline{Software Engineer (Contractor)}}{Remote} \resumeItemListStart
  \resumeItem{\normalsize{Worked on the canvas rendering system — added theme/mode switching, auto-pan, visual component grid, and element inspector; helped fix canvas loading bugs for new users.}}
  \resumeItem{\normalsize{Added chat features including slash command menu, clear chat, Claude health checks, and helped improve message send performance and clipboard handling.}}
  \resumeItem{\normalsize{Helped set up Storybook across 4 repos (fiddle, shadcn-ui, eleven-labs-ui, design-engineer) — wrote stories for UI primitives and added MutationObserver-based content readiness detection.}}
  \resumeItem{\normalsize{Worked on build pipeline — integrated Storycap-based screenshot system, post-commit build triggers, and ripgrep-powered search.}}
  \resumeItem{\normalsize{Helped add access control with allowlist, user types, template restrictions, and PKCE auth flow for the dashboard.}}
  \resumeItem{\normalsize{Fixed 15+ bugs and DX issues — toast migration (react-toastify to sonner), eslint react-hooks cleanup, double-submission prevention, and loading state improvements.}}
  \resumeItemListEnd \resumeSubHeadingListEnd
  \vspace{-12pt}

  \resumeSubHeadingListStart \resumeSubheading {fiddle-factory \href{https://github.com/fiddle-factory}{\raisebox{-0.1\height}{\faExternalLink} }}{May 2025 -- Aug 2025}
  {\underline{Software Engineer Intern}}{Remote} \resumeItemListStart \resumeItem{\normalsize{Migrated the canvas system from react-flow to tldraw — removed previous node implementation and added custom shapes, tools, preview components, and data conversion utilities.}}
  \resumeItem{\normalsize{Migrated the cloud sandbox from StackBlitz WebContainers to e2b — set up custom templates, API config, sandbox session management, and documented the environment.}}
  \resumeItem{\normalsize{Worked on the Figma-to-code plugin — helped set up the codegen pipeline, multi-frame export, and tweakpane UI integration.}}
  \resumeItem{\normalsize{Helped build the user onboarding flow with interactive checklist, task tooltips, and progress tracking.}}
  \resumeItem{\normalsize{Contributed to the "make real" feature — added API route, response shapes, and integrated canvas drawings as chat attachments.}}
  \resumeItemListEnd \resumeSubHeadingListEnd
  \vspace{-12pt}
\end{document}